---
title: "Crosstalk Practice"
output: 
  html_document:
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r pkg-load}
library(dplyr)
library(ggplot2)
library(plotly)
library(DT)
library(leaflet)
library(crosstalk)
```

```{r data-load}
trips <- readRDS("../data/trips_apr.rds")
stations <- readRDS("../data/stations.rds")
```

## Inspect the Datsets

To practice `crosstalk`, we will use two data sets. 

The `trips` data set contains one row per (a sample of) subway station. It includes many variables that summarize the number of rides in April 2019 and April 2020. 

The `stations` dataset contains one row per (a sample of) subway station. It contains metadata about each station, such as its longitude and latitude.

```{r}
head(trips)
head(stations)
```

## Warm-Up

To warm-up, we can look at a static visualization of the `trips` dataset.

```{r}
gg_trips <- 
  ggplot(data = trips) +
  aes(
    x = year_2019,
    y = year_2020
  ) +
  geom_point()

gg_trips
```

Using `plotly`, we can make this plot interactive with features such as a tooltip and zooming. 

```{r}
ggplotly(gg_trips)
```

## Interactive Viz with one `SharedData` object

Now, let's make two plots based on the `trips` data set. We will link them by `station_id` so that we can understand more elements of a single stations behavior at once. 

```{r}
# make SharedData object ----
trips_ct <- SharedData$new(trips, key = ~station_id)

# make ggplots using SharedData object ----
gg_year <-
  ggplot(trips_ct) +
  aes(x = year_2019, y = pct_change, col = pct_change) +
  geom_point()
  
gg_week <- 
  ggplot(trips_ct) +
  aes(x = prop_wend_2019, y = prop_wend_2020, col = pct_change) +
  geom_point()
  
# convert ggplots to ggplotly ----
gg_year_ly <- ggplotly(gg_year)
gg_week_ly <- ggplotly(gg_week)

# compose output ----
bscols(gg_year_ly, gg_week_ly)
```

## Interactive Viz with different widgets 

We can combine different types of widgets in the same way that we combine two plots. Now, let's try this by changing out second plot to instead be an interactive table.

```{r}
# make SharedData object ----
trips_ct <- SharedData$new(trips, key = ~station_id)

# make ggplots using SharedData object ----
gg_year <-
  ggplot(trips_ct) +
  aes(x = year_2019, y = pct_change, col = pct_change) +
  geom_point()

# make htmlwidgets ----
gg_year_ly <- ggplotly(gg_year)
dt_stations <- datatable(trips_ct)

# compose output ----
bscols(gg_year_ly, dt_stations)
```

## Interactive Viz with two `SharedData` objects

If we need to use data from multiple data sets, we can link them with the `group` argument when creating the `SharedData` objects. We will use this trick to turn our table into a map, which requires the `stations` data set for the latitude and longitude.

```{r}
# make SharedData object ----
trips_ct <- SharedData$new(trips, key = ~station_id, group = "group")
stations_ct <- SharedData$new(stations, key = ~station_id, group = "group")

# make ggplots with SharedData object ----
gg_year <-
  ggplot(trips_ct) +
  aes(x = year_2019, y = pct_change, col = pct_change) +
  geom_point()
  
# make htmlwidgets ----
gg_year_ly <- ggplotly(gg_year)
lf_station <- leaflet(stations_ct) %>% addTiles() %>% addMarkers()

# compose output ----
bscols(gg_year_ly, lf_station)
```

