---
title: "`crosstalk` Formative Assessment"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(palmerpenguins)
library(ggplot2)
library(plotly)
library(crosstalk)
knitr::opts_chunk$set(echo = FALSE)
```

## Multiple Choice

Consider a `penguins` data set with columns: `r paste(names(penguins), collapse = ", ")`. 

Suppose we plan to make multiple plots which we want to interact based on the `island` variable. 

```{r mult-choice}
question("Which of the following is the correct way to create the SharedData object?",
  answer("penguins_ct <- SharedData$new(penguins, group = 'island')"),
  answer("penguins_ct <- SharedData$new(penguins)"),
  answer("penguins_ct <- SharedData$new(penguins, key = ~island)", correct = TRUE),
  answer("penguins_ct <- SharedData$new(penguins, key = 'island')")
)
```


## Fill in the Blank

Consider a `penguins` data set with columns: `r paste(names(penguins), collapse = ", ")`. 

Fill in the blanks (`---`) in the following code in order to make two side-by-side scatterplots. 

The left plot should show bill length (`bill_length_mm`) versus bill depth (`bill_depth_mm`), and the second should show flipper length (`flipper_length_mm`) versus body mass (`body_mass_g`). When any point is clicked, all data points for that species should be highlighted. 

All relevant packages have already been loaded.

```{r blanks, exercise=TRUE}
penguins_ct <- SharedData$new(penguins, key = ~---)

gg_bill <- ggplot(---) + aes(bill_length_mm, bill_depth_mm) + geom_point()
gg_flip <- ggplot(---) + aes(flipper_length_mm, body_mass_g) + geom_point()

gg_bill_ly <- ggplotly(gg_bill)
gg_flip_ly <- ggplotly(gg_flip)

---(gg_bill_ly, gg_flip_ly)
```


```{r blanks-solution}
penguins_ct <- SharedData$new(penguins, key = ~species)

gg_bill <- ggplot(penguins_ct) + aes(bill_length_mm, bill_depth_mm) + geom_point()
gg_flip <- ggplot(penguins_ct) + aes(flipper_length_mm, body_mass_g) + geom_point()

gg_bill_ly <- ggplotly(gg_bill)
gg_flip_ly <- ggplotly(gg_flip)

bscols(gg_bill_ly, gg_flip_ly)
```
